{$\ch_2(\tf)$ Optimality Conditions for a Finite-time Horizon\thanksref{mytitlenote}}

### 2019-04-03 FH Optimality Conditions Paper.tex
fixed equations to fit in double column format

%\documentclass[preprint]{elsarticle}
\documentclass[twocolumn]{autart}  
\usepackage{graphics, euscript, float,blkarray, listings}
\usepackage {graphicx}
%\usepackage[top = 1 in, bottom = 1 in, right = 1 in, left = 1 in]{geometry}
\usepackage{tabularx, booktabs, array, float, framed}
\usepackage{color} %red, green, blue, yellow, cyan, magenta, black, white
\usepackage{appendix, setspace}
\usepackage{mathtools}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\definecolor{mygreen}{RGB}{28,172,0} % color values Red, Green, Blue
\definecolor{mylilas}{RGB}{170,55,241}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{mathtools,thmtools,etoolbox}
\usepackage{algorithm,algorithmicx,algpseudocode}
\usepackage{booktabs,subcaption}
\usepackage{tikz,pgfplots}%\pgfplotsset{compat=1.14}
\pgfplotsset{compat=newest}
\usepackage{lineno}
\usepackage{todonotes}
\usepackage[colorlinks,citecolor=black]{hyperref}
%\usepackage{cleveref}
\usepackage[scientific-notation=true]{siunitx}
\usepackage{multicol}
\usepackage[font={large}]{caption}
\usepackage{subcaption}
%\usepackage{natbib}

%%%%%%%%%%%%%%%%%%%%%%%
%% `Elsevier LaTeX' style

% Theorem definitions
\newtheorem{theorem}{Theorem}[section]
%\crefname{theorem}{theorem}{theorems}
%\Crefname{theorem}{Theorem}{Theorems}

%\newtheorem{prop}[theorem]{Proposition}
%\crefname{prop}{proposition}{propositions}
%\Crefname{prop}{Proposition}{Propositions}

\newtheorem{lemma}[theorem]{Lemma}
%\crefname{lemma}{lemma}{lemmas}
%\Crefname{lemma}{Lemma}{Lemmas}

\newtheorem{corollary}[theorem]{Corollary}
%\crefname{corollary}{corollary}{corollaries}
%\Crefname{corollary}{Corollary}{Corollaries}

\theoremstyle{remark}
\theoremstyle{definition}
\newtheorem{remark}[theorem]{Remark}
\AtEndEnvironment{remark}{\hfill\ensuremath{\diamondsuit}}
%\crefname{remark}{remark}{remarks}
%\Crefname{remark}{Remark}{Remarks}
%
%\theoremstyle{definition}
%\newtheorem{defn}[theorem]{Definition}
%\crefname{defn}{definition}{definitions}
%\Crefname{defn}{Definition}{Definitions}

\newtheorem{example}[theorem]{Example}
\AtEndEnvironment{example}{\hfill\ensuremath{\bigcirc}}
%\crefname{example}{example}{example}
%\Crefname{example}{Example}{Examples}

% End theorem definitions

%% Some bold vectors
\newcommand{\bfell}{{\boldsymbol{\ell}}}
\newcommand{\bfphi}{{\boldsymbol{\phi}}}
\newcommand{\bflambda}{{\boldsymbol{\lambda}}}
\newcommand{\bfu}{{\boldsymbol{u}}}
\newcommand{\bfb}{{\boldsymbol{b}}}
\newcommand{\bfc}{{\boldsymbol{c}}}
\newcommand{\bfp}{{\boldsymbol{p}}}
\newcommand{\bfx}{{\boldsymbol{x}}}
\newcommand{\bfy}{{\boldsymbol{y}}}
\newcommand{\bfr}{{\boldsymbol{r}}}
\newcommand{\bff}{{\boldsymbol{f}}}
\newcommand{\bfe}{{\boldsymbol{e}}}
\newcommand{\bfg}{{\boldsymbol{g}}}
\newcommand{\bfv}{{\boldsymbol{v}}}
\newcommand{\bfw}{{\boldsymbol{w}}}
\newcommand{\bfV}{{\boldsymbol{V}}}
\newcommand{\bfW}{{\boldsymbol{W}}}
\newcommand{\bfF}{{\boldsymbol{F}}}
\newcommand{\bfG}{{\boldsymbol{G}}}
\newcommand{\bfpsi}{{\boldsymbol{\psi}}}
\newcommand{\bfpi}{{\boldsymbol{\pi}}}
\newcommand{\bfbeta}{{\boldsymbol{\beta}}}

%% Makros for figure legends
\newcommand{\original}{Original}
\newcommand{\loewner}{Loewner}
\newcommand{\additional}{Additional points}
\newcommand{\hermite}{Hermite}

%%%% Makros for the paper %%%%%%%%%
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\diag}{diag}
\DeclareMathOperator{\spann}{span}
\def\numData{n}
\def\leftDir{{\boldsymbol{\ell}}}
\def\LeftDir{\mathcal{L}}
\def\leftPoint{\mu}
\def\LeftPoint{\mathcal{M}}
\def\leftData{{\boldsymbol{f}}}
\def\LeftData{\mathcal{F}}
\def\rightDir{{\boldsymbol{\it r}}}
\def\RightDir{\mathcal{R}}
\def\rightPoint{\sigma}
\def\RightPoint{\mathcal{S}}
\def\rightData{{\boldsymbol{g}}}
\def\RightData{\mathcal{G}}
\def\bitangentialData{\theta}
% Realization and Reduced Matrices
\def\numFunctions{K}
\def\Hred{\smash{\widetilde{H}}}
\def\Ered{\smash{\widetilde{E}}}
\def\Ared {\smash{\widetilde{A}}}
\def\Bred{\smash{\widetilde{B}}}
\def\Cred{\smash{\widetilde{C}}}
\def\Kred{\smash{\widetilde{\mathcal{K}}}}
\def\xred{\widetilde{\boldsymbol{x}}}
\def\yred{\widetilde{\boldsymbol{y}}}
% Full model
\def\dimFOM{N}

%\newcommand{\e}[1]{\mathrm{e}^{#1}}
\newcommand{\goyal}{GR}

%%%% END Macros for the paper %%%%%%%%%

\def\mathcal{\EuScript}

\numberwithin{equation}{section}
\newtheorem{Theorem}{Theorem}[section]
\newtheorem{Lemma}[Theorem]{Lemma}
\newtheorem{Definition}[Theorem]{Definition}
\newtheorem{Proposition}[Theorem]{Proposition}
\newcommand{\FH}{FHIRKA}
\newcommand{\R}{\mathbb{R}}
\newcommand{\bh}{\hat{B}}
\newcommand{\hc}{\hat{C}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\x}{\mathbf{x}}
\newcommand{\A}{\mathbf{A}}
\newcommand{\bpi}{\mathbf{\Pi}}
\newcommand{\Y}{\mathbf{Y}}
\newcommand{\E}{\mathbf{E}}
\newcommand{\B}{\mathbf{B}}
\newcommand{\I}{\mathbf{I}}
\newcommand{\G}{\mathbf{G}}
\newcommand{\C}{\mathbf{C}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\X}{\mathbf{X}}
\newcommand{\U}{\mathbf{U}}
\newcommand{\K}{\mathbf{K}}
\newcommand{\T}{\mathbf{T}}
\newcommand{\y}{\mathbf{y}}
\newcommand{\f}{\mathbf{f}}
\newcommand{\uu}{\mathbf{u}}
\newcommand{\HH}{\mathbf{H}}
\newcommand{\PP}{\mathbf{P}}
\newcommand{\Q}{\mathbf{Q}}
\newcommand{\J}{\mathcal{J}}
\newcommand{\h}{\mathbf{h}}
\newcommand{\g}{\mathbf{g}}
\newcommand{\V}{\mathbf{V}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\tf}{t_f}
\newcommand{\rr}{\mathbf{r}}
\newcommand{\lb}{\mathbf{l}}
\newcommand{\rc}{\boldsymbol{r}}
\newcommand{\lc}{\boldsymbol{\ell}}
\newcommand{\cc}{\boldsymbol{c}}
\newcommand{\bb}{\boldsymbol{b}}
\newcommand{\ch}{\mathcal{H}}
\newcommand{\ca}{\mathcal{A}}
\newcommand{\cp}{\mathcal{P}}
\newcommand{\cl}{\mathcal{L}}
\newcommand{\cu}{\mathcal{U}}
\newcommand{\cq}{\mathcal{Q}}
\newcommand{\co}{\mathcal{O}}
\newcommand{\Si}{\mathbf{\Sigma}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcolumntype{x}[1]{>{\centering\arraybackslash\hspace{0pt}}p{#1}}
\newcommand{\pder}[2][]{\dfrac{\partial#1}{\partial#2}}
\newcommand{\cbfF}{\mbox{\boldmath${\EuScript{F}}$} }
\newcommand{\cbfH}{\mbox{\boldmath${\EuScript{H}}$} }
\newcommand{\cbfK}{\mbox{\boldmath${\EuScript{K}}$} }
\newcommand{\cbfBsm}{\mbox{{\scriptsize \boldmath${\EuScript{B}}$}}}
\newcommand{\cbfCsm}{\mbox{{\scriptsize \boldmath${\EuScript{C}}$}}}
\newcommand{\cbfD}{\mbox{\boldmath${\EuScript{D}}$}}
\newcommand{\cbfDsm}{\mbox{{\scriptsize \boldmath${\EuScript{D}}$}}}
\newcommand{\cbfW}{\mbox{\boldmath${\EuScript{W}}$} }
\newcommand{\cbfZ}{\mbox{\boldmath${\EuScript{Z}}$} }
\newcommand{\cbfI}{\mbox{${\EuScript{I}}$} }
\newcommand{\cbfA}{\mbox{${\EuScript{A}}$} }
\newcommand{\cbfB}{\mbox{${\EuScript{B}}$}}
\newcommand{\cbfC}{\mbox{${\EuScript{C}}$}}
\newcommand{\cbfG}{\mbox{${\EuScript{G}}$} }
\newcommand{\cbfV}{\mbox{${\EuScript{V}}$} }

%\biboptions{numbers,sort&compress}

\begin{document}

@@

\end{frontmatter}
%Introduction
\section{Introduction}
Simulation, design, and control of dynamical systems play an important role in numerous scientific and industrial tasks such as signal propagation in the nervous system, heat dissipation, prediction of major weather events. The need for  detailed  models due to the increasing demand for greater resolution leads to  
large-scale dynamical systems, posing tremendous computational difficulties when applied in numerical simulations. In order to overcome these challenges, we perform  model reduction where we replace the large-scale dynamics with high-fidelity reduced representations.

Consider the linear time-invariant dynamical system:
\begin{equation}  \label{fom1}
\begin{array}{rcl}
\dot{\x}(t) & =& \A\x(t) +\B\uu(t)\\
\y(t)&=&\C\x(t) 
\end{array}
%~~\mbox{with}~~ \x(0) = \mathbf{0},
\; \Leftrightarrow \;
\y(t)=\int_{0}^{t}\h (t-\tau)\uu(\tau) d\tau,
\end{equation}
\noindent
where $  \x(0) = \mathbf{0}, \A \in \R^{n\times n}$, $\B\in \R^{n\times m}$, and $\C\in \R^{p\times n}$ are constant matrices; 
the variable $\x(t)\in \R^n$ denotes the internal variables, $\uu(t)\in \R^m$ denotes the control inputs, and $\y(t)\in \R^p$ denotes the outputs; and $\h(t)=\C e^{\A t}\B$ is the impulse response of the full model.   The length of the internal variable $\x(t)$, i.e., $n$, is called the order of the full model that we would like to reduce.  Model
reduction achieves this by replacing the original model with a lower dimensional one:
\begin{equation}  \label{rom1}
\begin{array}{rcl}
\dot{\x}_r(t) & =& \A_r\x_r(t) +\B_r\uu(t)\\
\y_r(t)&=&\C_r\x_r(t) 
\end{array}
%~~\mbox{with}~~ \x_r(0) = \mathbf{0},
\; \Leftrightarrow \;
\y_r(t)=\int_{0}^{t}\h_r (t-\tau)\uu(\tau) d\tau,
\end{equation}
where as in \eqref{fom1}, $\x_r(0) = \mathbf{0}, \h_r(t)=\C_r e^{\A_r t}\B_r$ is the impulse response of the reduced model, and $\A_r \in \R^{r\times r}$, $\B_r\in \R^{r\times m}$, and $\C_r\in \R^{p\times r}$ with $r\ll n$. The goal is that the output of the reduced model, $\y_r(t)$, approximates the true output, $\y(t)$, of the original system accurately in an appropriate norm.

For the linear dynamical systems we consider here, a plethora of methods exists
for producing high-fidelity/optimal reduced models, such as  balanced truncation \cite{MulR76, Moo81} and its variants, optimal Hankel norm approximation \cite{Glo84}, and the Iterative Rational Krylov Algorithm (IRKA) \cite{GugBA08} and its variants; see \cite{Ant05,BauBF14} for further references.
These methods usually focus on constructing high-quality reduced models  over an infinite time horizon. However, in various settings, we might either have access to simulations over a finite horizon or can only simulate the system under investigation for a finite horizon such as in the case of unstable dynamical systems. Therefore, in those situations we are interested in the behavior of the dynamical system over a finite time interval $[0,t_f]$ where $t_f < \infty$, and we need the reduced model to be accurate only in the interval of interest.

Time-limited balanced truncation \cite{GawJ90, GugA03, RedK17, Kur17} and Proper Orthogonal Decomposition (POD)   \cite{HolLB96}  are two common frameworks to create reduced models on a finite horizon. 
For time-limited balanced truncation, \cite{GugA03} establishes an upper bound for the $\ch_\infty$ error between the full and reduced models,  \cite{RedK17} provides an $\ch_2$ error bound. In this paper,  we explore $\ch_2(\tf)$ optimality for model reduction over a finite time horizon. 
  We establish $\ch_2(\tf)$ optimality conditions over a finite time horizon and introduce an algorithm which yields better approximations of the large-scale dynamical systems compared to other model reduction methods.

@@

%Error Measures
\section{$\ch_2$-Optimal Model Reduction: The Infinite Horizon Case} \label{sec:intro}
Model reduction with respect to the $\ch_2$ norm in the infinite horizon case has been studied extensively; see, for examples, \cite{BarCO91,BryC90, FulO90, MeiL67, Hal92, HylB85, SpaMM92, YanL99, LepMPV91, GugBA08,AniBGA13,Wil70, vuillemin2014poles,CasL18, panzer2013, gerstner2007hom, VanGA08, breiten2013near} and the references therein. 
In this section, we briefly recall these results as they will help to highlight the similarities to and differences from the finite-horizon case that we are interested in.

@@

%Interpolatory Model Reduction
\subsection{Interpolatory Conditions for Optimal $\ch_2$ Model Reduction}
Given a reduced order $r$, the goal is to construct a reduced order model whose transfer function $\HH_r(s)$ minimizes the $\ch_2$ error norm $\norm{\HH - \HH_r}_{\ch_2}$.  Since this is a non-convex optimization problem, the usual, numerically feasible, approach  is to find a reduced model that satisfies the necessary conditions for $\ch_2$ optimality. These conditions can be formulated in terms of Sylvester equations 
\cite{Wil70,HylB85} or interpolation \cite{MeiL67, GugBA08}. These two frameworks are equivalent \cite{GugBA08}. In this paper, we will focus on the interpolation framework.
\begin{theorem} \label{h2thm}%{\text{\cite {MeiL67, GugBA08}}}
Let 
$$
\h_r(t)=\sum_{k=1}^r e^{\lambda_kt}\lc_k\rc_k^T \qquad \Longleftrightarrow \qquad \HH_r(s) = \sum_{k=1}^r \frac{\lc_k\rc_k^T}{s-\lambda_k}
$$
be the best $r^{th}$ order approximation of an asymptotically stable linear dynamical system  $\HH(s)$ with respect to the $\ch_2$ norm. Then, for $k=1, 2, ... , r$,
\begin{align} \label{eqn:h2cond}
\lc_k^T\HH(-\lambda_k)=\lc_k^T\HH_r(-\lambda_k),~~
\HH(-\lambda_k)\rc_k=\HH_r(-\lambda_k)\rc_k,~~\mbox{and},~~
\lc_k^T\HH'(-\lambda_k)\rc_k=\lc_k^T\HH_r'(-\lambda_k)\rc_k.
\end{align}
\end{theorem}
{\color{red}For more details on theorem \ref{h2thm}, see {\cite {MeiL67, GugBA08}}.}
This result states that the transfer function of the optimal $\ch_2$ approximation to $\HH(s)$ is a (tangential) Hermite interpolant where the interpolation points are the mirror images of the reduced-order poles $\{\lambda_k\}$, and the tangental directions are given by the corresponding residues $\{\lc_k\rc_k^T\}$. {\color{red} Throughout this paper, we denote the derivative of $\HH(s)$ by $\HH'(s)$.} Since the optimality conditions depend on the reduced-model to be computed, the solution requires a nonlinear iteration. The Iterative Rational Krylov Algorithm (IRKA)  \cite{GugBA08} and its variants such as \cite{beattie2012realization,gerstner2007hom,CasL18,beattie2009trust} use these interpolation based optimality conditions to produce   an interpolatory, locally $\ch_2$ optimal reduced model. The next section will extend this framework to the finite-time interval case.

@@

%Error measures in a finite-time horizon
\subsection{$\ch_2(t_f)$ Norm on a Finite-time Horizon}
It is immediately clear from the time-domain definition of the (infinite-horizon) $\ch_2$ norm how to define the finite-horizon version:
\begin{Definition}\label{innerh2}
Let $\h(t)$ and $\g(t)$ denote the impulse responses of two dynamical systems with real state-space realizations.  
For a finite-time horizon 
$[0,t_f]$, the $\ch_2(\tf)$ inner product $\langle \cdot, \cdot \rangle_{\ch_2(\tf)}$ 
and $\ch_2(\tf)$ norm $\norm{\cdot}_{\ch_2(\tf)}$ are defined as  
\begin{align*}
\langle \h, \g \rangle_{\ch_2(\tf)} =\int_0^{\tf} \mathsf{Tr}( (\h(t))^T \g(t)) dt \quad \mbox{and}\quad
\norm{\h}_{\ch_2(\tf)} =\sqrt{\int_0^{\tf} \norm{\h(t)}_F^2 dt},
\end{align*} 
respectively.
\end{Definition}

@@

It is immediately clear that, the $\ch_2(t_f)$-error satisfies 
\begin{equation}\label{merexp}
\begin{aligned}
\norm{\h-\h_r}_{\ch_2({\tf})}^2=\norm{\h}_{\ch_2({\tf})}^2-2 \langle\h, \h_r\rangle_{\ch_2({\tf})}+\norm{\h_r}_{\ch_2({\tf})}^2,
\end{aligned}
\end{equation}
where the inner product  $\langle\h, \h_r\rangle_{\ch_2({\tf})}$ is real since $\h(t)$ and $\h_r(t)$ are real. Finding the first-order necessary conditions for optimal ${\ch_2({\tf})}$ model reduction will require computing the gradient of the error expression \eqref{merexp} with respect to the optimization variables. 
Since the reduced model, as described by  the impulse response in $\h_r(t)$, is parametrized by the 
reduced order poles $\{\lambda_i\}$, and the residue directions $\{\lc_i\}$ and $\{\rc_i\}$, we will be computing the gradient of the error with respect to these variables. Since the first term in the error \eqref{merexp}, i.e., $\norm{\h}_{\ch_2({\tf})}$, is a constant, we will be focusing on the remaining two terms only. First, in the next lemma, we will formulate these two last terms in terms of $\{\lambda_i\}$, 
$\{\lc_i\}$ and $\{\rc_i\}$.
\begin{Lemma}\label{minnerexp}

>>>>

%\documentclass[preprint]{elsarticle}
\documentclass[twocolumn]{autart}  
\input{paperPreamble}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\setlength{\headsep}{0pt}
\setlength{\topskip}{0pt}
\setlength{\topmargin}{0pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}
\begin{document}

@@

\end{frontmatter}
%Introduction
\section{Introduction}
Simulation, design, and control of dynamical systems play an important role in numerous scientific and industrial tasks such as signal propagation in the nervous system\cite{Steve Cox}, heat dissipation, prediction of major weather events \cite{BoyP11,Sha03,Ant05}. The need for  detailed  models due to the increasing demand for greater resolution leads to  
large-scale dynamical systems, posing tremendous computational difficulties when applied in numerical simulations. In order to overcome these challenges, we perform  model reduction where we replace the large-scale dynamics with high-fidelity reduced representations.

Consider the linear time-invariant dynamical system:
\begin{equation}  \label{fom1}
\begin{array}{rcl}
\dot{\x}(t) & =& \A\x(t) +\B\uu(t)\\
\y(t)&=&\C\x(t) 
\end{array}
%~~\mbox{with}~~ \x(0) = \mathbf{0},
\; \Leftrightarrow \;
\y(t)=\int_{0}^{t}\h (t-\tau)\uu(\tau) d\tau,
\end{equation}
\noindent
where $  \x(0) = \mathbf{0}, \A \in \R^{n\times n}$, $\B\in \R^{n\times m}$, and $\C\in \R^{p\times n}$ are constant matrices; 
the variable $\x(t)\in \R^n$ denotes the internal variables, $\uu(t)\in \R^m$ denotes the control inputs, and $\y(t)\in \R^p$ denotes the outputs; and $\h(t)=\C e^{\A t}\B$ is the impulse response of the full model.   The length of the internal variable $\x(t)$, i.e., $n$, is called the order of the full model that we would like to reduce.  Model
reduction achieves this by replacing the original model with a lower dimensional one:
\begin{equation}  \label{rom1}
%\begin{array}{rcl}
\begin{aligned}
\dot{\x}_r(t)&=\A_r\x_r(t)+\B_r\uu(t)\\
\y_r(t)&=\C_r\x_r(t) 
\end{aligned}
%\end{array}
%~~\mbox{with}~~ \x_r(0) = \mathbf{0},
\; \Leftrightarrow \;
\y_r(t)=\int_{0}^{t}\h_r (t-\tau)\uu(\tau)d\tau,
\end{equation}
where as in \eqref{fom1}, $\x_r(0) = \mathbf{0}, \h_r(t)=\C_r e^{\A_r t}\B_r$ is the impulse response of the reduced model, and $\A_r \in \R^{r\times r}$, $\B_r\in \R^{r\times m}$, and $\C_r\in \R^{p\times r}$ with $r\ll n$. The goal is that the output of the reduced model, $\y_r(t)$, approximates the true output, $\y(t)$, of the original system accurately in an appropriate norm.

For the linear dynamical systems we consider here, a plethora of methods exists
for producing high-fidelity/optimal reduced models, such as  balanced truncation \cite{MulR76,Moo81} and its variants, optimal Hankel norm approximation \cite{Glo84}, and the Iterative Rational Krylov Algorithm (IRKA) \cite{GugBA08} and its variants; see \cite{Ant05,BauBF14} for further references.
These methods usually focus on constructing high-quality reduced models  over an infinite time horizon. However, in various settings, we might either have access to simulations over a finite horizon or can only simulate the system under investigation for a finite horizon such as in the case of unstable dynamical systems. Therefore, in those situations we are interested in the behavior of the dynamical system over a finite time interval $[0,t_f]$ where $t_f < \infty$, and we need the reduced model to be accurate only in the interval of interest.

Time-limited balanced truncation \cite{GawJ90,GugA03,RedK17,Kur17} and Proper Orthogonal Decomposition (POD)   \cite{HolLB96}  are two common frameworks to create reduced models on a finite horizon. 
For time-limited balanced truncation, \cite{GugA03} establishes an upper bound for the $\ch_\infty$ error between the full and reduced models,  \cite{RedK17} provides an $\ch_2$ error bound. In this paper,  we explore $\ch_2(\tf)$ optimality for model reduction over a finite time horizon. 
  We establish $\ch_2(\tf)$ optimality conditions over a finite time horizon and introduce an algorithm which yields better approximations of the large-scale dynamical systems compared to other model reduction methods.

@@

%Error Measures
\section{$\ch_2$-Optimal Model Reduction: The Infinite Horizon Case} \label{sec:intro}
Model reduction with respect to the $\ch_2$ norm in the infinite horizon case has been studied extensively; see, for examples, \cite{BarCO91,BryC90,FulO90,MeiL67,Hal92,HylB85,SpaMM92,YanL99,LepMPV91,GugBA08,AniBGA13,Wil70,vuillemin2014poles,CasL18,panzer2013,gerstner2007hom,VanGA08,breiten2013near} and the references therein. 
In this section, we briefly recall these results as they will help to highlight the similarities to and differences from the finite-horizon case that we are interested in.

@@

%Interpolatory Model Reduction
\subsection{Interpolatory Conditions for Optimal $\ch_2$ Model Reduction}
Given a reduced order $r$, the goal is to construct a reduced order model whose transfer function $\HH_r(s)$ minimizes the $\ch_2$ error norm $\norm{\HH - \HH_r}_{\ch_2}$.  Since this is a non-convex optimization problem, the usual, numerically feasible, approach  is to find a reduced model that satisfies the necessary conditions for $\ch_2$ optimality. These conditions can be formulated in terms of Sylvester equations \cite{Wil70,HylB85} or interpolation \cite{MeiL67,GugBA08}. These two frameworks are equivalent \cite{GugBA08}. In this paper, we will focus on the interpolation framework.
\begin{theorem} \label{h2thm}%{\text{\cite {MeiL67, GugBA08}}}
Let 
$$
\h_r(t)=\sum_{k=1}^r e^{\lambda_kt}\lc_k\rc_k^T \qquad \Longleftrightarrow \qquad \HH_r(s) = \sum_{k=1}^r \frac{\lc_k\rc_k^T}{s-\lambda_k}
$$
be the best $r^{th}$ order approximation of an asymptotically stable linear dynamical system  $\HH(s)$ with respect to the $\ch_2$ norm. Then, for $k=1, 2, ... , r$,
\begin{equation} \label{eqn:h2cond}
\begin{aligned}
\lc_k^T\HH(-\lambda_k)&=\lc_k^T\HH_r(-\lambda_k),\\~~
\HH(-\lambda_k)\rc_k&=\HH_r(-\lambda_k)\rc_k,\\
\lc_k^T\HH'(-\lambda_k)\rc_k&=\lc_k^T\HH_r'(-\lambda_k)\rc_k.
\end{aligned}
\end{equation}
\end{theorem}
{\color{red}For more details on theorem \ref{h2thm}, see {\cite {GugBA08}}.}
This result states that the transfer function of the optimal $\ch_2$ approximation to $\HH(s)$ is a (tangential) Hermite interpolant where the interpolation points are the mirror images of the reduced-order poles $\{\lambda_k\}$, and the tangental directions are given by the corresponding residues $\{\lc_k\rc_k^T\}$. {\color{red} Throughout this paper, we denote the derivative of $\HH(s)$ by $\HH'(s)$.} Since the optimality conditions depend on the reduced-model to be computed, the solution requires a nonlinear iteration. The Iterative Rational Krylov Algorithm (IRKA)  \cite{GugBA08} and its variants such as \cite{beattie2012realization,gerstner2007hom,CasL18,beattie2009trust} use these interpolation based optimality conditions to produce   an interpolatory, locally $\ch_2$ optimal reduced model. The next section will extend this framework to the finite-time interval case.

@@

%Error measures in a finite-time horizon
\subsection{$\ch_2(t_f)$ Norm on a Finite-time Horizon}
It is immediately clear from the time-domain definition of the (infinite-horizon) $\ch_2$ norm how to define the finite-horizon version:
\begin{Definition}\label{innerh2}
Let $\h(t)$ and $\g(t)$ denote the impulse responses of two dynamical systems with real state-space realizations.  
For a finite-time horizon 
$[0,t_f]$, the $\ch_2(\tf)$ inner product $\langle \cdot, \cdot \rangle_{\ch_2(\tf)}$ 
and $\ch_2(\tf)$ norm $\norm{\cdot}_{\ch_2(\tf)}$ are defined as  
\begin{align*}
\langle \h, \g \rangle_{\ch_2(\tf)} &=\int_0^{\tf} \mathsf{Tr}( (\h(t))^T \g(t)) dt, \\%\quad \mbox{and}\quad
\norm{\h}_{\ch_2(\tf)} &=\sqrt{\int_0^{\tf} \norm{\h(t)}_F^2 dt}.
\end{align*}

\end{Definition}

@@

It is immediately clear that, the $\ch_2(t_f)$-error satisfies 
\begin{equation}\label{merexp}
\begin{aligned}
%\scalemath{0.9}
{
\norm{\h-\h_r}_{\ch_2({\tf})}^2=\norm{\h}_{\ch_2({\tf})}^2-2 \langle\h, \h_r\rangle_{\ch_2({\tf})}+\norm{\h_r}_{\ch_2({\tf})}^2,
}
\end{aligned}
\end{equation}
where the inner product  $\langle\h, \h_r\rangle_{\ch_2({\tf})}$ is real since $\h(t)$ and $\h_r(t)$ are real. Finding the first-order necessary conditions for optimal ${\ch_2({\tf})}$ model reduction will require computing the gradient of the error expression \eqref{merexp} with respect to the optimization variables. 
Since the reduced model, as described by  the impulse response in $\h_r(t)$, is parametrized by the 
reduced order poles $\{\lambda_i\}$, and the residue directions $\{\lc_i\}$ and $\{\rc_i\}$, we will be computing the gradient of the error with respect to these variables. Since the first term in the error \eqref{merexp}, i.e., $\norm{\h}_{\ch_2({\tf})}$, is a constant, we will be focusing on the remaining two terms only. First, in the next lemma, we will formulate these two last terms in terms of $\{\lambda_i\}$, 
$\{\lc_i\}$ and $\{\rc_i\}$.
\begin{Lemma}\label{minnerexp}

Let  $\h (t)= \sum_{j=1}^n e^{\rho_jt} \cc_j \bb_j^T $ and $\h_r(t) = \sum_{i=1}^r e^{\lambda_it}\lc_i  \rc_i^T $ be, respectively, the impulse responses of the full and reduced models  as described in \eqref{eqn:hfull} and \eqref{kernel2}.
Then,
\begin{align} \label{eqn:hhr}
\langle\h, \h_r\rangle_{\ch_2({\tf})}=\sum_{j=1}^n\sum_{i=1}^r\lc_{i}^T\cc_j\bb_j^T\rc_{i}\dfrac{e^{(\lambda_i+\rho_j){\tf}}-1}{\lambda_i+\rho_j},
\end{align}
and
\begin{align} \label{eqn:hrhr}
\norm{\h_r}_{\ch_2({\tf})}^2= \sum_{i=1}^r\sum_{j=1}^r\lc_{i}^T\lc_{j}\rc_{j}^T\rc_{i}\dfrac{e^{(\lambda_i+\lambda_j){\tf}}-1}{\lambda_i+\lambda_j}.
\end{align}
\end{Lemma}
\begin{pf}
The both results  follow from the definition of the $\ch_2(\tf)$ inner product.  First consider
\begin{align*}
\langle\h, \h_r\rangle_{\ch_2({\tf})}&=\mathsf{Tr}\left(\int_0^{\tf}\h_r(t)^T\h(t)\, dt\right).
\end{align*}
Plug $\h (t)= \sum_{j=1}^n \cc_j \bb_j^T e^{\rho_jt}$ and $\h_r(t) = \sum_{i=1}^r \lc_i  \rc_i^T e^{\lambda_it}$
into this formula to obtain
\begin{align*}
%\begin{dmath*}
\langle\h, \h_r\rangle_{\ch_2({\tf})}&=\mathsf{Tr} \left(\int_0^{\tf}\sum_{i=1}^r(\lc_{i}\rc_{i}^Te^{\lambda_it})^T\sum_{j=1}^n\cc_j\bb_j^Te^{\rho_jt}dt\right)\\
 &= \mathsf{Tr} \left(\sum_{i=1}^r 
\sum_{j=1}^n 
\rc_{i}\lc_{i}^T\cc_j \bb_j^T \int_0^{\tf}e^{(\lambda_i + \rho_j )t} dt\right)
%\end{dmath*}
\end{align*}
Computing the integral and using the fact that $\mathsf{Tr}(\A_1 \A_2) = \mathsf{Tr}(\A_2 \A_1)$  for two matrices $\A_1$ and $\A_2$ of  appropriate sizes,   we obtain
\begin{align*}
\langle\h, \h_r\rangle_{\ch_2({\tf})}&=\mathsf{Tr}\left(\sum_{j=1}^n\sum_{i=1}^r\rc_{i}\lc_{i}^T\cc_j\bb_j^T\dfrac{e^{(\lambda_i+\rho_j){\tf}}-1}{\lambda_i+\rho_j}\right)\\
&=\sum_{j=1}^n\sum_{i=1}^r\lc_{i}^T\cc_j\bb_j^T\rc_{i}\dfrac{e^{(\lambda_i+\rho_j){\tf}}-1}{\lambda_i+\rho_j},
\end{align*}
which proves \eqref{eqn:hhr}. Then, \eqref{eqn:hrhr} follows directly by replacing $\h(t)$ with $\h_r(t)$ in this derivation. 
\end{pf}
For infinite time horizon, Theorem \ref{h2thm} tells us that a locally $\ch_2$ optimal reduced transfer function is a tangential Hermite interpolant of the original transfer function at the mirror images of the reduced poles. We will show that in the finite horizon case, even though Hermite tangential interpolation is still the necessary conditions for optimality,  what is being interpolated and what the interpolant is are different.
